### 2023-12-08 supporting.tex
Put supplement panel labels on separate lines for readability
Added a respectively to clarify a figure caption
Updated figure references to PLoS style

\begin{figure}[h!]
\includegraphics[width=\textwidth]{substitution/out/heatmap_ematrix.png}
\centering
\caption{\textbf{Exchangeability matrices fit to meta-alignments yielded by different sampling strategies.}
Each panel is a mean of the exchangeability coefficients fit to the meta-alignments yielded by a single sampling strategy ($n = 25$). The prefix and suffix in the title of each panel indicate the maximum gap fraction and region type of the columns in the meta-alignments. For example, the columns in the ``50R\_disorder'' set of meta-alignments were fewer than 50\% gaps and sampled from the disorder regions.}
\label{sfig:heatmap_ematrix}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{substitution/out/heatmap_rmatrix.png}
\centering
\caption{\textbf{Rate matrices fit to meta-alignments yielded by different sampling strategies.}
Each panel is a mean of the rate coefficients fit to the meta-alignments yielded by a single sampling strategy ($n = 25$). See Fig.~\ref{sfig:heatmap_ematrix} for an explanation of the panel labels.}
\label{sfig:heatmap_rmatrix}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{substitution/out/heatmap_corr.png}
\centering
\caption{\textbf{Correlations between mean exchangeability and rate matrices fit to meta-alignments yielded by different sampling strategies.}
\textbf{(A)} Correlations between the mean exchangeability matrices in Fig.~\ref{sfig:heatmap_ematrix}. \textbf{(B)} Correlations between the mean rate matrices in Fig.~\ref{sfig:heatmap_rmatrix}.}
\label{sfig:heatmap_corr}
\end{figure}

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{substitution/out/heatmap_ematrix.png}
\centering
\caption{\textbf{Exchangeability matrices fit to meta-alignments yielded by different sampling strategies.}
Each panel is a mean of the exchangeability coefficients fit to the meta-alignments yielded by a single sampling strategy ($n = 25$). The prefix and suffix in the title of each panel indicate the maximum gap fraction and region type of the columns in the meta-alignments, respectively. For example, the columns in the ``50R\_disorder'' set of meta-alignments were fewer than 50\% gaps and sampled from the disorder regions.}
\label{sfig:heatmap_ematrix}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{substitution/out/heatmap_rmatrix.png}
\centering
\caption{\textbf{Rate matrices fit to meta-alignments yielded by different sampling strategies.}
Each panel is a mean of the rate coefficients fit to the meta-alignments yielded by a single sampling strategy ($n = 25$). See \ref{sfig:heatmap_ematrix}~Fig for an explanation of the panel labels.}
\label{sfig:heatmap_rmatrix}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{substitution/out/heatmap_corr.png}
\centering
\caption{\textbf{Correlations between mean exchangeability and rate matrices fit to meta-alignments yielded by different sampling strategies.}
\textbf{(A)} Correlations between the mean exchangeability matrices in \ref{sfig:heatmap_ematrix}~Fig.
\textbf{(B)} Correlations between the mean rate matrices in \ref{sfig:heatmap_rmatrix}~Fig.}
\label{sfig:heatmap_corr}
\end{figure}
